\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-15 paper.tex
started variable assignment, continue at operators

    \subsubsection{Variable Assignment}
    \subsubsection{While Loop}

>>>>

    \subsubsection{Variable Assignment}

    Variable assignment will take place in two forms where the right side of the assignment can be either just a variable or a combination of two variables with a comparison or an arithmetic operator in between. The assignment format is: a variable name, a space, a colon, an equality operator, a space and the right side (a variable name or a variable name, a space, an operator, a space, another variable name). The implementation of the first case of variable assignment is presented below:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    parse_assignment_var :: Parse AST
    parse_assignment_var = 
        isword `bind` \leftvar -> tokenize " := " 
               `bind` \eq -> isword 
               `bind` \rightvar -> 
        result (AssignmentVar leftvar rightvar)

    \noindent The second case of variable assignment is not as simple as the first one since some additional parsers need to be included in order to parse operators (\textit{comparison} and \textit{arithmetic}).

    \subsubsection{While Loop}
